Homicide Increases in the COVID-19 Era

### 2025-02-25 Draft1.qmd
ggplot code

## ggplot2 ideas

* histogram (we did a barplot)
* boxplots! - 
* geom_tile - correlations - Bianca
* geom_jitter

>>>>

# ggplot2 ideas

## Histogram

## Boxplot - Kaitlyn

```{r}
crime_by_area <- crime_la %>% group_by(AREA.NAME) %>% summarize(numberOfCrimes = n()) %>% ungroup()

bureaus <- read.csv("Raw_Data/Division_Bureau_Ref.csv")

bureaus$Division <- gsub("77th", "77th Street", bureaus$Division)
bureaus$Division <- gsub("North", "N", bureaus$Division)
bureaus$Division <- gsub("Neast", "Northeast", bureaus$Division)

crime_by_area <- crime_by_area %>% left_join(bureaus, join_by("AREA.NAME" == "Division"))
```

## geom_tile for correlations - Bianca

## geom_jitter
